---
title: "RWorksheet_Leysa#4b"
author: "Camilo Leysa"
date: "2024-10-28"
output: pdf_document
---

1. for loop
```{r}
vectorA <- c(1,2,3,4,5)
Amatrix <- matrix(0, nrow=5, ncol=5)

for (i in 1:5){
  for (j in 1:5) {
    Amatrix[i,j] <- abs(i-j)
  }
}

Amatrix
```
2. Print "*" using for() function
```{r}
for (i in 1:5){
  cat(rep("*",i),"\n")
}
```

3. Get an Input from user to print Fibonacci Sequence from 1st input to 500
```{r} 
#start_num <- as.numeric(readline(prompt = "Enter a number from 1-500: "))
#  a <- start_num
#  b <- start_num + 1
  
#  while (b <500) {
#    cat(a," ")
#    next_numb <- a+b
#    a <- b
#    b<- next_numb
#  }
  
#  cat("\n")

#I make this chunk to a comment because this actually runs, however,when I knit it,
#it stops from knitting to pdf because it says that the while loop needs a true or false.
```
4. Import the dataset of Sizes,Height,Gender.csv
```{r}
data_list <- read.table("Sizes,Height,Gender.csv", sep = ",", header = TRUE)
data_list
```
4a. Display the first 6 rows
```{r}
head(data_list,6)
```
4b. Subset for male and female
```{r}
data_of_male <- subset(data_list,Gender == "M")
data_of_female <- subset(data_list, Gender == "F")
cat("Male:", nrow(data_of_male), "\nFemale:", nrow(data_of_female), "\n")
```
4c.Graph of numbers of males and females in household data
```{r}
hdata <- read.table("HouseholdData.csv", sep = ",", header = TRUE)
hdata
barplot(table(hdata$Sex), col = c("blue","pink"), main = "Gender Distribution",xlab = "Sex", ylab = "Count")
```
5a. Pie Chart for Dela Cruz Family
```{r}
expenses <- c(Food=60, Electricity=10,Savings=5,Miscellaneous=25)
percentage <- paste0(names(expenses),"(", round(expenses/sum(expenses)*100,1),"%)")
pie(expenses, labels= percentage, main = "Dela Cruz Family Monthly Spending", col=rainbow(length(expenses)))
```
6a.Dataset of Iris
```{r}
data(iris)
str(iris)
```
6b. Mean ofsepals and petals (length & width)
```{r}
means <- colMeans(iris[,1:4])
means
```
6c. Pie Chart of Species Distribution
```{r}
pie(table(iris$Species), main = "Species Distribution", col=c("purple","orange","green"))
```
6d. Subsets of Species
```{r}
Setosa <- tail(subset(iris, Species == "setosa"),6)
VersiColor <- tail(subset(iris, Species == "versicolor"),6)
Virginica <- tail(subset(iris, Species == "virginica"),6)

Setosa
VersiColor
Virginica
```
6e. Scatterplot
```{r}
plot(iris$Sepal.Length, iris$Sepal.Width, col=iris$Species, pch=19, main = "Iris Dataset", xlab="Sepal Length", ylab="Sepal Width", sub = "Sepal Width and Length")
legend("topright", legend=levels(iris$Species), col = 1:3, pch=19)
```
6f.
```{r}
#Based on the scatter plot show, the Setosa is the most distinct species, and it can also
#be identified by its shorter sepal length and greater sepal width. On the other hand, the
#Versicolor and Virginica have more similar sepal dimensions because they have at least 
#similar length and width of sepal, and in order to distinguish their difference, they need
# additional features, like petal measurements, in order to give us an accurate classification
# of these two species.
```

7.
```{r}
library(readxl)
alexadata <- read.table("alexa_file.xlsx", sep = ",", header = TRUE)
alexadata
```


















