---
title: "RWorksheet_Leysa#4a"
author: "Camilo Leysa"
date: "2024-10-14"
output: pdf_document
---
1.
a. The table below shows the data about shoe size and height. Create a data frame.
   Describe the data.
```{r}
sizes_shoe<- data.frame(Shoe_size=c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5,13.0
                                    ,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0),
                        Height=c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,
                                 71.0,77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,
                                 69.0,70.0), 
                        Gender=c("F","F","F","F","M","F","F","F","M","F","M","F","M","M","M","M","F",
                                 "F","M","F","F","M","M","F","M","M","M","M"))
sizes_shoe
```
b. Create a subset by males and females with their corresponding shoe size and height.
```{r}
male_subset <- subset(sizes_shoe,Gender =="M")
male_subset
```
b.
```{r}
female_subset <- subset(sizes_shoe,Gender == "F")
female_subset
```

c. Find the mean of the shoe size of the respondents.
```{r}
mean_shoesize <- mean(sizes_shoe$Shoe_size)
mean_shoesize
```
c.  Find the mean of the height of the respondents. 
```{r}
mean_height <- mean(sizes_shoe$Height)
mean_height
```

d. Is there a relationship between shoe size and height? Why?
```{r}
#There is a relationship in the shoe size and height. As we can see in the table, if a person is
#tend to be taller, its shoe size is also big. For instance, we can see in the person with the
#height of 77.0 has also a big shoe size of 13.0. This implies that the taller individuals often
#have larger feet which generally aligns with their biological expectations.
```

2.
a.Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months_vector <- c("March","April","January","November","January","September","October",
                   "September","November","August","January","November","November","February",
                   "May","August","July","December","August","August","September","September",
                   "November","February","April")
factor_months_vector <- factor(months_vector)
factor_months_vector
```

3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?

```{r}
summary_months <- summary(months_vector)
summary_months
```
```{r}
summary_factor_months <- summary(factor_months_vector)
summary_factor_months
```
4. Create a vector and factor for the table below.
```{r}
Directions <- c("East","West","North")
Frequency<- c(1L,4L,3L)
Directions
Frequency
new_order_data <- factor(Directions, levels= c("East","West","North"))
new_order_data
```

5. Enter the data below in Excel with file name = import_march.csv
```{r}
Data <- read.table("import_march.csv", sep=",", header = TRUE)
Data
```
b.View the dataset. Write the R scripts and its result.

```{r}
View(Data)
```







