---
title: "RWorksheet_Leysa#4c"
author: "Camilo Leysa"
date: "2024-11-04"
output: pdf_document
---

1.
a. Show your solution on how to import a csv file on your environment.
```{r}
library(ggplot2)
mpg_data <- read.csv("mpg.csv")
mpg_data
```
b. Which variables from the mpg dataset are categorical?
```{r}
#The variables that are categorical in the mpg dataset are manufacturer, model, year,
#cyl, trans, drv, fl and class.
```

c. Which variables from the mpg dataset are continuous?
```{r}
#The variables that are continuous in the mpg dataset are displ, cty and hwy.
```

2. Manufacturer with the most models.
```{r}
library(dplyr)
m_model <- mpg_data %>% group_by(manufacturer) %>% summarise(m_model = n_distinct(model))
m_model
```

2a. Group the manufacturers and find the unique models.
```{r}
library(tidyr)
uniqueness <- mpg_data %>% group_by(manufacturer) %>% summarise(unique_models = list(unique(model))) %>% unnest(unique_models)
uniqueness
```

2b. Graph the result using plot() and ggplot().
```{r}
#plot
#plot(m_model$manufacturer, m_model$m_model, xlab = "Manufacturer", ylab = "Unique Models")

#ggplot2
ggplot(m_model, aes(x=manufacturer, y=m_model)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x = "Manufacturer", y= "Number of Unique Models")
```

2. Relationship of the model and the manufacturer.
a.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
b. Useful or not?
```{r}
# Although the code is better because it shows a plot, however, I cannot understand 
# the relationship of the 2 data. So, in order for the data to be informative, I will
# filter the top models, use summarized data or choose other data that has a
# significant relationship with other data.
```

3. Plotting the model and the year using ggplot() using top 20 observations.
```{r}
library(ggplot2)
top_20 <- mpg_data %>% slice_head(n=20)
ggplot(top_20, aes(x = model, y = year)) + geom_point() +theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x = "Model", y = "Year" )
```

4. Using the %>% to group the model and the number of cars per model.
```{r}
car_per_model <- mpg_data %>% group_by(model) %>% summarise(count = n())
car_per_model
```

4a. Plotting using geom_bar with 20 observations
```{r}
ggplot(car_per_model %>% slice_head(n = 20), aes(x = reorder(model, count), y = count)) + geom_bar(stat = "identity", fill = "steelblue") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x = "Model", y = "Number of Cars")
```

b. Plot using coord_flip().
```{r}
ggplot(car_per_model %>% slice_head(n = 20), aes(x = reorder(model, count), y = count)) + geom_bar(stat = "identity", fill = "purple") + coord_flip() + labs(x = "Model", y = "Number of Cars")
```
5. Plotting the relationship of cylinders and displacement (cyl and displ)
```{r}
ggplot(mpg_data, aes(x = cyl, y = displ, color = displ)) + geom_point() + labs(title = "Relationship between No. of Cylinders and Engine Displacement", x = "Numbers of Cylinders", y = "Engine Displacement")
```

6. Plotting the relationship between displ(engine displacement) and hwy (highway miles per gallon)
```{r}
ggplot(mpg_data, aes(x = displ, y = hwy)) + geom_point() + labs(x = "Engine Displacement (L)", y = "Highway Miles per Gallon")
```

6. Importing traffic.csv
```{r}
traffic<- read.csv("traffic.csv")
traffic
```
6a. Numbers of observation
```{r}
print(dim(traffic))
print(names(traffic))
```

6b. Subset the traffic dataset into junctions.
```{r}
junction_traffic <- subset(traffic, Junction == "your_junction_condition")
junction_traffic
```

6c. Plot with geom_line()
```{r}
ggplot(traffic, aes(x = DateTime, y = Vehicles)) + geom_line() + labs(x = "Time", y = "Traffic Volume")
```
7.import alexa_file.xlsx
```{r}
library(readxl)
alexa <- read_excel("alexa_file.xlsx")
alexa
```

7a. Number of observations of alexa
```{r}
print(dim(alexa))
```

7b. Group the variations and get the total of each variations.
```{r}
total_variation <- alexa %>% group_by(variation) %>% summarise(total = n())
total_variation
```

7c. Plotting the variations
```{r}
ggplot(total_variation, aes(x = variation, y = total)) + geom_bar(stat = "identity") + labs(x = "Variation", y = "Total Count")
```

7d. Plotting using geom_line.
```{r}
ggplot(alexa, aes(x = date, y = verified_reviews)) + geom_line() +labs(x = "Date", y = "Verified Reviews")
```

7e. Getting the relationship of Variations and Ratings.
```{r}
ggplot(alexa, aes(x = variation, y = rating)) + geom_boxplot() + labs(x = "Variation", y = "Rating")
```






















